Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
tweak abstract

XXX

>>>>

Meta-tracing JITs can be applied to a variety of different
languages without explicitly encoding language semantics into the compiler. So
far, they lacked a way to feed back runtime information into the
compiler, which restricted their performance. In this paper we describe the
flexible mechanisms in PyPy's meta-tracing JIT that can be used to control runtime feedback in language-specific ways. These mechanisms are flexible
enough to implement classical VM techniques such as maps and polymorphic inline
caches.
